Digital History in Finland, 1488-1828

### 2016-07-07 inst/examples/20160715-slides-Krakow.Rmd
switched to combined data

```{r 201606krakow-init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Read data
fen0 <- readRDS("fennica.Rds")
kun0 <- readRDS("kungliga.Rds")

fenraw <- readRDS("fennica.raw.Rds")
kunraw <- readRDS("kungliga.raw.Rds")

fen <- fen0 %>% filter(publication_year >= min.year & publication_year <= max.year)
kun <- kun0 %>% filter(publication_year >= min.year & publication_year <= max.year)

# Full time span
df.full = bind_rows(fen0, kun0)
df.full$catalog = factor(c(rep("Fennica", nrow(fen0)), rep("Kungliga", nrow(kun0))))

# Selected time spam
df0 = bind_rows(fen, kun)
df0$catalog = factor(c(rep("Fennica", nrow(fen)), rep("Kungliga", nrow(kun))))
```

@@

```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
df <- fen %>%
  filter(publication_year >= 1640 & publication_year <= 1800)%>% 
      filter(!is.na(country)) %>%
      filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01)

@@

>>>>

```{r 201606krakow-init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Full combined catalogue (Fen + Kun) with marked duplicates
df.combined.preprocessed <- readRDS("df.combined.Rds")
# Data with duplicates removed
df.full <- df.combined.preprocessed %>% filter(!remove)
# Data with years limited as well
df0 <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
```

@@

```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
df <- subset(df0, catalog == "Fennica") %>%
  filter(publication_year >= 1640 & publication_year <= 1800)%>% 
      filter(!is.na(country)) %>%
      filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01)

@@

```{r duplicates, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
# DUPLICATE FRACTION
df <- df.combined.preprocessed %>% group_by(catalog) %>%
      			           summarise(duplicates = 100 * mean(remove))
p <- ggplot(df, aes(x = catalog, y = duplicates)) +
       geom_bar(position = "dodge", stat = "identity") +
       ylab("Duplicates (%)") +
       ggtitle(paste("Duplicates", paste(range(df.combined.preprocessed$publication_year), collapse = "-")))
print(p)
```

### 2016-07-07 inst/examples/manuscript-krakow.Rmd
switched to combined data

# Read data
fen0 <- readRDS("df.Rds")
kun0 <- readRDS("../../../kungliga/df.Rds")

fenraw <- readRDS("df.raw.Rds")
kunraw <- readRDS("../../../kungliga/df.raw.Rds")

fen <- fen0 %>% filter(publication_year >= min.year & publication_year <= max.year)
kun <- kun0 %>% filter(publication_year >= min.year & publication_year <= max.year)

# Full time span
df.full = bind_rows(fen0, kun0)
df.full$catalog = factor(c(rep("Fennica", nrow(fen0)), rep("Kungliga", nrow(kun0))))

# Selected time spam
df0 = bind_rows(fen, kun)
df0$catalog = factor(c(rep("Fennica", nrow(fen)), rep("Kungliga", nrow(kun))))

>>>>

# Read data
#fen0 <- readRDS("df.Rds")
#kun0 <- readRDS("../../../kungliga/df.Rds")

#fenraw <- readRDS("df.raw.Rds")
#kunraw <- readRDS("../../../kungliga/df.raw.Rds")

#fen <- fen0 %>% filter(publication_year >= min.year & publication_year <= max.year)
#kun <- kun0 %>% filter(publication_year >= min.year & publication_year <= max.year)

# Full time span
#df.full = bind_rows(fen0, kun0)
#df.full$catalog = factor(c(rep("Fennica", nrow(fen0)), rep("Kungliga", nrow(kun0))))

# Selected time spam
#df0 = bind_rows(fen, kun)
#df0$catalog = factor(c(rep("Fennica", nrow(fen)), rep("Kungliga", nrow(kun))))

# Full combined catalogue (Fen + Kun) with marked duplicates
df.combined.preprocessed <- readRDS("df.combined.Rds")
# Data with duplicates removed
df.full <- df.combined.preprocessed %>% filter(!remove)
# Data with years limited as well
df0 <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
